Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-10-24 demystify.tex
updates

\begin{itemize}
    \item \textbf{Not customizing the email, too generic}: a copy and paste kind of email or those that can be sent to multiple professors with very little modifications. This shows the lack of interest and will be treated as spam.  
    \item \textbf{Self-focus} You focus too much about you and your achievements but not why you are interested in the prof.'s work (\autoref{sec:contact}). Why their work is interesting and how your background fits in.
    \item \textbf{Too long}. Keep it to about 3--4 paragraphs. Seriously, less is more and long emails are often not read and discarded.\\
    Personally I do not want to see course transcript or CV in the first email.  If we are interested, we will ask for more information.
    \item \textbf{Flowery greetings and language}. Don't use ``Dear esteemed professor'', ``kindly consider my application'', etc. And of course, don't ``hey there''. 
    \item \textbf{Sending the similar mail to multiple profs}. Sending emails to multiple profs. using BCC or even CC (where we can see all addresses the email is being sent to) will result in no reply or a very harsh one on how unprofessional this is.
    \item \textbf{Not being professional}, e.g., do not call the professor by their first name in the first email (some don't care but you don't want to take the risk -- you don't know them that well yet).  Do not use Mr., Mrs., etc. Use Prof. Lastname or Dr. Lastname (\autoref{sec:address}).
    \item \textbf{Ignoring the Prof's guideline} and asking questions that are already answered on their website (most CS profs have personal websites). For example, on my website, I put very specific information on how to contact me (e.g., email subject).
    \item \textbf{Fancy format}. CS people like plain text.  Do not use colors, fonts, or fancy formats.
\end{itemize}

>>>>

\begin{itemize}
    \item \textbf{Not customizing the email, too generic}: a copy and paste kind of email or those that can be sent to multiple professors with very little modifications. This shows the lack of interest and will be treated as spam.  
    \item \textbf{Self-focus} You focus too much about you and your achievements but not why you are interested in the prof.'s work (\autoref{sec:contact}). Why their work is interesting and how your background fits in.
    \item \textbf{Too long}. Keep it to about 3--4 paragraphs. Seriously, less is more and long emails are often not read and discarded.\\
    Personally I do not want to see course transcript or CV in the first email.  If we are interested, we will ask for more information.
    \item \textbf{Flowery greetings and language}. Don't use ``Dear esteemed professor'', ``kindly consider my application'', etc. And of course, don't ``hey there''. 
    \item \textbf{Not being professional}, e.g., do not call the professor by their first name in the first email (some don't care but you don't want to take the risk -- you don't know them that well yet).  Do not use Mr., Mrs., etc. Use Prof. Lastname or Dr. Lastname (\autoref{sec:address}).
    \item \textbf{Ignoring the Prof's guideline} and asking questions that are already answered on their website (most CS profs have personal websites). For example, on my website, I put very specific information on how to contact me (e.g., email subject).
    \item \textbf{Fancy format}. CS people like plain text.  Do not use colors, fonts, or fancy formats.
    \item \textbf{Mass emails}. This is too obvious but I've seen it many times when a student mass emails all profs in a department (e.g., through CC or even BCC---we know because faculty talk to each other).  This will result in no reply or a very harsh one on how unprofessional you are.
\end{itemize}
